\documentclass[letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage{amsmath,amssymb,amsthm,dsfont}
\usepackage{setspace,parskip,multicol,titling}

\newcommand{\R}{\mathds{R}}
\newcommand{\Z}{\mathds{Z}}
\newcommand{\Q}{\mathds{Q}}
\newcommand{\C}{\mathds{C}}

\newcommand{\nope}{\textbf{DO THIS}}
\newcommand{\group}[1]{\langle \, #1 \, \rangle}
\renewcommand{\b}[1]{\textbf{#1}}

\setlength{\droptitle}{-1cm}
\setlength\parindent{30pt}
\setlength\parskip{8pt}
\setstretch{1.50}
\setlist{leftmargin=0.25in}

\title{CSC 258 Project 1}
\author{Brandon Willett}

\begin{document}

	\maketitle

	\begin{enumerate}[1)]

		\item \begin{enumerate}[a)]

			\item \begin{itemize}

				\item For the \texttt{small-1} graph, there are eleven tasks on the critical path, namely 268, 253, 249, 241, 234, 223, 219, 210, 184, 120, 87 (in reverse order) which constitutes the total 231 time units.

				\item For the \texttt{small-2} graph, there are ten tasks on the critical path, namely 141, 139, 132, 129, 120, 109, 89, 87, 76, 49 (in reverse order) which constitutes the total 201 time units.

				\item For the \texttt{medium-1} graph, there are 23 tasks on the critical path (probably too many to list here).

				\item For the \texttt{large} graph, there are 38 tasks on the critical path (definitely too many to list here).

			\end{itemize}

			\item \begin{itemize}

				\item For the \texttt{small-1} graph, the smallest number of processors you can get away with while still having the same performance as you'd have in the infinite case is 68.

				\item For the \texttt{small-2} graph, the smallest number of processors you can get away with while still having the same performance as you'd have in the infinite case is 49.

				\item For the \texttt{medium-1} graph, there are 23 tasks on the critical path (probably too many to list here).

				\item For the \texttt{large} graph, there are 38 tasks on the critical path (definitely too many to list here).

			\end{itemize}

		\end{enumerate}

	\end{enumerate}

\end{document}